Metascatter: Unifying Symbiotic Radio and Intelligent Reflecting Surface

### 2022-07-12 main.tex
:pencil: Fix primary rate expression
:pencil: Update manuscript

\newacronym{af}{AF}{Amplify-and-Forward}
\newacronym{ambc}{AmBC}{Ambient Backscatter Communications}
\newacronym{ap}{AP}{Access Point}
\newacronym{awgn}{AWGN}{Additive White Gaussian Noise}
\newacronym{bcd}{BCD}{Block Coordinate Descent}
\newacronym{bibo}{BIBO}{Binary-Input Binary-Output}
\newacronym{bpcu}{\si{bpcu}}{bit per channel use}
\newacronym{bpsphz}{\si{bps/Hz}}{bit per second per Hertz}
\newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
\newacronym{csi}{CSI}{Channel State Information}
\newacronym{df}{DF}{Decode-and-Forward}
\newacronym{dmc}{DMC}{Discrete Memoryless Channel}
\newacronym{dmtc}{DMTC}{Discrete Memoryless Thresholding Channel}
\newacronym{dmtmac}{DMTMAC}{Discrete Memoryless Thresholding Multiple Access Channel}
\newacronym{dp}{DP}{Dynamic Programming}
\newacronym{iid}{i.i.d.}{independent and identically distributed}
\newacronym{irs}{IRS}{Intelligent Reflecting Surface}
\newacronym{kkt}{KKT}{Karush–Kuhn–Tucker}
\newacronym{mac}{MAC}{Multiple Access Channel}
\newacronym{mc}{MC}{Multiplication Coding}
\newacronym{miso}{MISO}{Multiple-Input Single-Output}
\newacronym{mimo}{MIMO}{Multiple-Input Multiple-Output}
\newacronym{ml}{ML}{Maximum-Likelihood}
\newacronym{noma}{NOMA}{Non-Orthogonal Multiple Access}
\newacronym{ofdm}{OFDM}{Orthogonal Frequency-Division Multiplexing}
\newacronym{pdf}{PDF}{Probability Density Function}
\newacronym{pgd}{PGD}{Projected Gradient Descent}
\newacronym{psk}{PSK}{Phase Shift Keying}
\newacronym{pin}{PIN}{Positive Intrinsic-Negative}
\newacronym{qam}{QAM}{Quadrature Amplitude Modulation}
\newacronym{rf}{RF}{Radio-Frequency}
\newacronym{sc}{SC}{Superposition Coding}
\newacronym{sic}{SIC}{Successive Interference Cancellation}
\newacronym{simo}{SIMO}{Single-Input Multiple-Output}
\newacronym{sinr}{SINR}{Signal-to-Interference-plus-Noise Ratio}
\newacronym{smawk}{SMAWK}{Shor-Moran-Aggarwal-Wilber-Klawe}
\newacronym{sr}{SR}{Symbiotic Radio}
\newacronym{tdma}{TDMA}{Time-Division Multiple Access}
\newacronym{tg}{TG}{tag}
\newacronym{ue}{UE}{user}

\begin{document}
\title{Metascatter: Unifying Symbiotic Radio and Intelligent Reflecting Surface}
\author{
	\IEEEauthorblockN{
		Yang~Zhao,~\IEEEmembership{Member,~IEEE,}
		and~Bruno~Clerckx,~\IEEEmembership{Senior~Member,~IEEE}
	}
	\thanks{
		The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: \{yang.zhao18, b.clerckx\}@imperial.ac.uk).
	}
}
\maketitle

\begin{abstract}
	% Backscatter allows wireless nodes to harvest energy from, modulate information over, and reconfigure propagation of surrounding radio waves.
	Passive backscatter nodes can harvest energy from, modulate information over, and reconfigure propagation of surrounding radio waves.
	We uniquely introduce the concept of Metascatter, which adapts the input distribution of a finite-state backscatter tag based on \gls{csi}, to \emph{simultaneously} encode self message and assist legacy transmission while powered by ambient signal.
	Compared to conventional \gls{irs}-empowered \gls{sr} that performs encoding and beamforming independently (overlay or parallel), Metascatter refines backscatter principles to bridge parasitic source of \gls{sr} and reflecting element of \gls{irs} as extreme cases.
	Such an integrated distribution design not only yields universal modularity with reduced optimization cost, but also enables a flexible tradeoff between primary and backscatter links using shared spectrum, energy, and infrastructures.
	To validate its benefits, we consider an application scenario where a multi-antenna \gls{ap} transmits to a single-antenna user surrounded by multiple Metascatters.
	For simplicity, the user is assumed first decodes all Metascatters jointly by energy detection, then models their contribution within equivalent channel and decodes the primary link.
	We characterize the achievable primary-(sum-)backscatter rate region through a joint optimization of input distribution at the Metascatters, transmit beamforming at the AP, and decision thresholds at the user.
	The problem is highly non-convex and we propose a suboptimal \gls{bcd} solution, where the input distribution satisfying the \gls{kkt} conditions is evaluated in closed form, the transmit beamforming is updated by \gls{pgd}, and the decision thresholds are optimized by \gls{dp}.
	Simulation results demonstrate Metascatters can exploit additional backscatter paths to coordinate transmit and assist via smart input design.
\end{abstract}

\begin{section}{Introduction}
	\IEEEPARstart{B}{ackscatter} is recently re-innovated as a promising approach to support low-power communications and control wireless propagation environments.
	The concept of \gls{ambc} was first proposed in \cite{Liu2013b}, where each tag harvests energy from and modulates information over ambient \gls{rf} signals by periodically switching between different reflection patterns.
	It enables battery-free communication between fully passive nodes, but the backscatter signal strength can be relatively weak and the decoding is subject to strong direct-link interference.
	To solve this, \cite{Yang2018d} exploited the repeating structure of \gls{ofdm} symbol for interference cancellation based on backscatter channel strength.
	Cooperative primary-backscatter decoding using co-located receiver, known as cooperative \gls{ambc}, was proposed in \cite{Yang2018}.
	The authors evaluated the error performance of \gls{ml}, linear, and \gls{sic} detectors for flat fading channels, and proposed a low-complexity \gls{ml} detector for frequency-selective fading channels with ambient \gls{ofdm} carrier.
	When transmit cooperation is also available, cooperative \gls{ambc} is more commonly known as \gls{sr} \cite{Liang2020}.
	The authors of \cite{Guo2019b} classified \gls{sr} into commensal, parasitic, and competitive modes based on the relative link priority, then derived their instantaneous achievable rate and optimal power allocation.
	The outage probability for those modes was later studied in \cite{Ding2020}.
	On the other hand, it was concluded in \cite{Long2020a} that if the backscatter symbol period is much longer than the primary symbol period, then the non-coherent achievable rate of primary decoding would approach that of the coherent case.
	The authors also considered the transmit precoder design for weighted sum-rate maximization and transmit power minimization problems.
	\cite{Zhou2019a} explored how the number of transmit antennas, receive antennas, and symbol period ratio asymptotically influence the ergodic rate of primary and backscatter links.
	With multi-antenna at all ends, \cite{Wu2021a} optimized the transmit precoder to maximize the backscatter achievable rate under primary rate constraint.
	However, those paper only considered single tag scenario and the optimal tag multiple access scheme remains unknown.
	\cite{Xu2021a} proposed a \gls{noma}-based \gls{sr} and studied the receive combiner design when the receiver decodes in the order of equivalent channel strength.
	A \gls{tdma}-based \gls{sr} with energy harvesting constraints was also presented in \cite{Yang2021a}, and energy efficiency maximization was considered with respect to transmit power, reflection efficiency, and time allocation design.
	In \cite{Han2021}, random code-assisted backscatter multiple access was combined with \gls{sr}, and the authors evaluated the asymptotic \gls{sinr} performance using random matrix theory.

@@

	\emph{Third,} we characterize the achievable primary-(sum-)backscatter rate region by iteratively optimizing the tag input distribution, the backscatter decision threshold, and the transmit precoder.
	For the input design, we propose a numerical method to evaluate the \gls{kkt} solutions by limits of sequences.
	For the threshold design, we derive the minimum number of decision thresholds to maximize the total backscatter rate, and obtain the optimal thresholds by \gls{dp} accelerated by \gls{smawk} algorithm.
	However, the optimal precoder design can be non-trivial and we may end up with a low-complexity suboptimal solution.

@@

\begin{section}{Backscatter Principles}
	% \begin{figure}[!t]
	% 	\centering
	% 	\subfloat[Block Diagram]{
	% 		\resizebox{0.6\columnwidth}{!}{
	% 			\input{assets/block_diagram.tex}
	% 		}
	% 		\label{fi:block_diagram}
	% 	}
	% 	\setcounter{subfigure}{2}%
	% 	\subfloat[Scatter Model]{
	% 		\resizebox{0.35\columnwidth}{!}{
	% 			\input{assets/scatter_model.tex}
	% 		}
	% 		\label{fi:scatter_model}
	% 	}
	% 	\setcounter{subfigure}{1}
	% 	\subfloat[Equivalent Circuit]{
	% 		\resizebox{0.95\columnwidth}{!}{
	% 			\input{assets/equivalent_circuit.tex}
	% 		}
	% 		\label{fi:equivalent_circuit}
	% 	}
	% 	\caption{Block diagram, equivalent circuit, and scatter model of a typical passive tag. The solid and dashed vectors represent signal and energy flows. The backscatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.}
	% \end{figure}

	\begin{figure}[!t]
		\centering
		\subfloat[Block Diagram]{
			\resizebox{0.8\columnwidth}{!}{
				\input{assets/block_diagram.tex}
			}
			\label{fi:block_diagram}
		}
		\\
		\subfloat[Equivalent Circuit]{
			\resizebox{0.95\columnwidth}{!}{
				\input{assets/equivalent_circuit.tex}
			}
			\label{fi:equivalent_circuit}
		}
		\\
		\subfloat[Scatter Model]{
			\resizebox{0.8\columnwidth}{!}{
				\input{assets/scatter_model.tex}
			}
			\label{fi:scatter_model}
		}
		\caption{Block diagram, equivalent circuit, and scatter model of a typical passive tag. The solid and dashed vectors represent signal and energy flows. The backscatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.}
	\end{figure}
	% In a bistatic backscatter system,
	% Consider a bistatic backscatter system with an excitation source, multiple passive tags, and a backscatter reader.
	Passive backscatter devices (a.k.a., tags) harvest energy from and modulate information over surrounding \gls{rf} signal.
	As shown in Fig. \subref*{fi:block_diagram}, a typical passive tag consists of a scattering antenna, an energy harvester, an integrated receiver, a load-switching modulator, and on-chip components (e.g., micro-controller and sensors) \cite{Dobkin2012}. Its equivalent circuit is also given by Fig. \subref*{fi:equivalent_circuit}.
	When illuminated, the tag absorbs a portion of the impinging wave and scatters the rest back to the space.
	The absorbed signal can be used for source decoding and energy harvesting \cite{Kim2021a}, while the scattered signal can be decomposed into the \emph{structural} and \emph{antenna} mode components \cite{Hansen1989}.
	The structural mode scattering applies to general objects and is related to the antenna structure, shape and material, which contributes to environment multipath and can be covered by channel estimation \cite{Boyer2014}.
	On the other hand, the antenna mode scattering models the antenna radiation and depends on the antenna-load impedance mismatch, which can be used for backscatter modulation \cite{Boyer2012} or channel reconfiguration \cite{Wu2021b}.
	Fig. \subref*{fi:scatter_model} illustrates the scatter model.
	For a tag with $M$ candidate states, the reflection coefficient of state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is defined as
	\begin{footnote}
		It corresponds to a linear backscatter model where the reflection coefficient is irrelevant to incident electromagnetic field strength.
	\end{footnote}
	\begin{equation}
		\Gamma_m = \frac{Z_m - Z_{\mathrm{A}}^*}{Z_m + Z_{\mathrm{A}}},
		\label{eq:reflection_coefficient}
	\end{equation}
	where $Z_m$ is the load impedance at state $m$ and $Z_{\mathrm{A}}$ is the antenna input impedance.

@@

		Once the tag input combination is successfully decoded, the backscatter uncertainty can be eliminated and the equivalent channel for primary transmission can be updated by \eqref{eq:equivalent_channel}.
		Similar to above, the primary information function of input combination $x_{m_{\mathcal{K}}}$ is
		% TODO notation
		\begin{equation}
			I_{\mathrm{P}}(x_{m_{\mathcal{K}}};\boldsymbol{y}) \triangleq N \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right),
			\label{eq:primary_information_function}
		\end{equation}
		the primary marginal information function associated with letter $x_{m_k}$ of tag $k$ is
		\begin{equation}
			I_{\mathrm{P},k}(x_{m_k};\boldsymbol{y}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I_{\mathrm{P}}(x_{m_{\mathcal{K}}};\boldsymbol{y}),
			\label{eq:primary_marginal_information_function}
		\end{equation}
		and the primary (ergodic) mutual information is
		\begin{equation}
			I_{\mathrm{P}}(x_{\mathcal{K}};\boldsymbol{y}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) N \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right).
			\label{eq:primary_mutual_information}
		\end{equation}

@@

\begin{section}{Input, Threshold, and Precoder Design}
	To characterize the achievable primary-(sum-)backscatter rate region of Metascatter, we aim to maximize the weighted sum mutual information with respect to tag input probability distribution $\{\boldsymbol{p}_k\}$, decision threshold vector $\boldsymbol{t}$, and transmit precoder $\boldsymbol{w}$
	\begin{maxi!}
		{\scriptstyle{\{\boldsymbol{p}_k\},\boldsymbol{t},\boldsymbol{w}}}{I(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y})}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
		\addConstraint{\sum \nolimits_{m_k} P_k(x_{m_k})}{=1,}{\quad \forall k \in \mathcal{K}}{\label{co:sum_probability}}
		\addConstraint{P_k(x_{m_k})}{\ge 0,}{\quad \forall k \in \mathcal{K}, \ \forall m_k \in \mathcal{M}}{\label{co:nonnegative_probability}}
		\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P.}{\label{co:transmit_power}}
	\end{maxi!}
	Since problem \eqref{op:weighted_sum_rate} is not jointly convex, we propose a \gls{bcd} algorithm that iteratively updates $\{\boldsymbol{p}_k\}$, $\boldsymbol{t}$ and $\boldsymbol{w}$ until convergence.

	\begin{subsection}{Input Probability Distribution}
		For any fixed decision boundary $\boldsymbol{t}$ and transmit precoder $\boldsymbol{w}$, the equivalent \gls{dmtmac} can be formulated by \eqref{eq:dmtmac} and problem \eqref{op:weighted_sum_rate} boils down to
		\begin{maxi!}
			{\scriptstyle{\{\boldsymbol{p}_k\}}}{I(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y})}{\label{op:input_probability_distribution}}{}
			\addConstraint{\eqref{co:sum_probability},\eqref{co:nonnegative_probability},}
		\end{maxi!}
		which involves the product term $\prod_{k \in \mathcal{K}} P_k(x_{m_k})$ and is non-convex when $K > 1$.
		Interestingly, the sum-rate optimal input design for general discrete memoryless \gls{mac} remains an open problem, and we instead propose a \gls{kkt} solution to problem \eqref{op:input_probability_distribution}.
		\begin{footnote}
			As pointed out in \cite{Buhler2011}, \gls{kkt} conditions are only necessary for sum-rate optimality and these solutions may end up being saddle points.
		\end{footnote}
		\begin{proposition}
			The \gls{kkt} optimality conditions for problem \eqref{op:input_probability_distribution} are equivalent to, $\forall k \in \mathcal{K}$ and $\forall m_k \in \mathcal{M}$,
			\begin{subequations}
				\label{eq:input_kkt_condition}
				\begin{alignat}{2}
					I_k^\star(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) & = I^\star(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y}), \quad   &  & P_k^\star(x_{m_k}) > 0,\label{eq:probable_states} \\
					I_k^\star(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) & \le I^\star(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y}), \quad &  & P_k^\star(x_{m_k}) = 0.\label{eq:dropped_states}
				\end{alignat}
			\end{subequations}
			\label{pr:input_kkt_condition}
		\end{proposition}

>>>>

\newacronym{af}{AF}{Amplify-and-Forward}
\newacronym{ambc}{AmBC}{Ambient Backscatter Communications}
\newacronym{ap}{AP}{Access Point}
\newacronym{awgn}{AWGN}{Additive White Gaussian Noise}
\newacronym{bcd}{BCD}{Block Coordinate Descent}
\newacronym{bibo}{BIBO}{Binary-Input Binary-Output}
\newacronym{bpcu}{\si{bpcu}}{bits per channel use}
\newacronym{bpsphz}{\si{bps/Hz}}{bits per second per Hertz}
\newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
\newacronym{csi}{CSI}{Channel State Information}
\newacronym{df}{DF}{Decode-and-Forward}
\newacronym{dmc}{DMC}{Discrete Memoryless Channel}
\newacronym{dmtc}{DMTC}{Discrete Memoryless Thresholding Channel}
\newacronym{dmtmac}{DMTMAC}{Discrete Memoryless Thresholding Multiple Access Channel}
\newacronym{dp}{DP}{Dynamic Programming}
\newacronym{iid}{i.i.d.}{independent and identically distributed}
\newacronym{irs}{IRS}{Intelligent Reflecting Surface}
\newacronym{kkt}{KKT}{Karush–Kuhn–Tucker}
\newacronym{mac}{MAC}{Multiple Access Channel}
\newacronym{mc}{MC}{Multiplication Coding}
\newacronym{miso}{MISO}{Multiple-Input Single-Output}
\newacronym{mimo}{MIMO}{Multiple-Input Multiple-Output}
\newacronym{ml}{ML}{Maximum-Likelihood}
\newacronym{noma}{NOMA}{Non-Orthogonal Multiple Access}
\newacronym{ofdm}{OFDM}{Orthogonal Frequency-Division Multiplexing}
\newacronym{pdf}{PDF}{Probability Density Function}
\newacronym{pgd}{PGD}{Projected Gradient Descent}
\newacronym{psk}{PSK}{Phase Shift Keying}
\newacronym{pin}{PIN}{Positive Intrinsic-Negative}
\newacronym{qam}{QAM}{Quadrature Amplitude Modulation}
\newacronym{rf}{RF}{Radio-Frequency}
\newacronym{sc}{SC}{Superposition Coding}
\newacronym{sic}{SIC}{Successive Interference Cancellation}
\newacronym{simo}{SIMO}{Single-Input Multiple-Output}
\newacronym{sinr}{SINR}{Signal-to-Interference-plus-Noise Ratio}
\newacronym{smawk}{SMAWK}{Shor-Moran-Aggarwal-Wilber-Klawe}
\newacronym{sr}{SR}{Symbiotic Radio}
\newacronym{tdma}{TDMA}{Time-Division Multiple Access}
\newacronym{tg}{TG}{tag}
\newacronym{ue}{UE}{user}

\begin{document}
\title{Metascatter: Unifying Symbiotic Radio and Intelligent Reflecting Surface}
\author{
	\IEEEauthorblockN{
		Yang~Zhao,~\IEEEmembership{Member,~IEEE,}
		and~Bruno~Clerckx,~\IEEEmembership{Fellow,~IEEE}
	}
	\thanks{
		The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: \{yang.zhao18, b.clerckx\}@imperial.ac.uk).
	}
}
\maketitle

\begin{abstract}
	% Backscatter allows wireless nodes to harvest energy from, modulate information over, and reconfigure propagation of surrounding radio waves.
	Backscatter nodes can harvest energy from, modulate information over, and reconfigure propagation of ambient signals.
	% Backscatter nodes can harvest energy from, modulate information over, and reconfigure propagation of surrounding radio waves.
	We uniquely introduce \emph{Metascatter} that adapts the input distribution of a finite-state passive backscatter node based on \gls{csi}, to \emph{simultaneously} encode self message and assist legacy transmission while powered by surrounding radio-frequency waves.
	% Compared to conventional \gls{irs}-empowered \gls{sr} that encodes and precodes independently (e.g., overlay or parallel), Metascatter refines backscatter principles to bridge parasitic source of \gls{sr} and reflecting element of \gls{irs} as extreme cases.
	Compared to existing \gls{irs}-empowered \gls{sr} that encodes and precodes independently using advanced architecture (e.g., overlay or parallel), Metascatter softly bridges and generalizes parasitic source of \gls{sr} and reflecting element of \gls{irs} via smart input design.
	% Compared to \gls{irs}-empowered \gls{sr} that encodes and precodes independently (e.g., overlay or parallel), Metascatter refines backscatter principles to bridge parasitic source of \gls{sr} and reflecting element of \gls{irs} as extreme cases.
	% Such an integrated distribution design not only yields universal modularity with reduced optimization cost, but also enables a flexible tradeoff between primary and backscatter links using shared spectrum, energy, and infrastructures.
	It not only reduces hardware complexity and optimization cost, but also enables a flexible tradeoff between primary and backscatter links using shared spectrum, energy, and infrastructures.
	Moreover, we consider an application scenario where a multi-antenna \gls{ap} serves a single-antenna user surrounded by multiple Metascatters.
	For simplicity, it is assumed the user first jointly decodes all backscatter messages based on average received power, then models reflection patterns and backscatter paths within equivalent channel for primary decoding.
	% Once modulation uncertainty of Metascatters are eliminated, models contributions from additional paths within equivalent channel
	% decodes all Metascatters jointly by energy detection, then models their contribution within equivalent channel and decodes the primary link.
	% For simplicity, the user is assumed first decodes all Metascatters jointly by energy detection, then models their contribution within equivalent channel and decodes the primary link.
	We characterize achievable primary-(total-)backscatter rate regions by jointly design input distribution at Metascatters, active beamforming at AP, and decision regions at user.
	% A suboptimal \gls{bcd} algorithm was proposed, where the input distribution satisfying the \gls{kkt} conditions is evaluated in closed form, the transmit beamforming is optimized by \gls{pgd}, and the decision thresholds are optimized by \gls{dp}.
	A suboptimal \gls{bcd} algorithm was proposed, where the \gls{kkt} input distribution is evaluated in closed form, the active beamforming is optimized by \gls{pgd} with backtracking line search, and convex decision regions are refined by \gls{dp}.
	% the decision regions are restricted as convex then optimized by \gls{dp}.
	% A suboptimal \gls{bcd} algorithm was proposed, where the \gls{kkt} input distribution is evaluated in closed form, the active beamforming is optimized by \gls{pgd} with backtracking line search, and the decision thresholds are optimized by \gls{dp}.
	Simulation results demonstrate Metascatters can exploit additional propagation paths to transmit and assist via input design.
\end{abstract}

\begin{section}{Introduction}
	\IEEEPARstart{B}{ackscatter} is recently re-innovated as a promising approach to support low-power communications and control wireless propagation environments.
	% The concept of \gls{ambc} was first proposed in \cite{Liu2013b}, where battery-free communication between passive nodes was established by
	\gls{ambc} that enables battery-free communication between passive nodes was first proposed in \cite{Liu2013b}, where battery-free communication between passive nodes was established by

	Battery-free communication between passive nodes was first by

	each tag harvests energy from and modulates information over ambient \gls{rf} signals by periodically switching between different reflection patterns.
	It enables battery-free communication between fully passive nodes, but the backscatter signal strength can be relatively weak and the decoding is subject to strong direct-link interference.
	To solve this, \cite{Yang2018d} exploited the repeating structure of \gls{ofdm} symbol for interference cancellation based on backscatter channel strength.
	Cooperative primary-backscatter decoding using co-located receiver, known as cooperative \gls{ambc}, was proposed in \cite{Yang2018}.
	The authors evaluated the error performance of \gls{ml}, linear, and \gls{sic} detectors for flat fading channels, and proposed a low-complexity \gls{ml} detector for frequency-selective fading channels with ambient \gls{ofdm} carrier.
	When transmit cooperation is also available, cooperative \gls{ambc} is more commonly known as \gls{sr} \cite{Liang2020}.
	The authors of \cite{Guo2019b} classified \gls{sr} into commensal, parasitic, and competitive modes based on the relative link priority, then derived their instantaneous achievable rate and optimal power allocation.
	The outage probability for those modes was later studied in \cite{Ding2020}.
	On the other hand, it was concluded in \cite{Long2020a} that if the backscatter symbol period is much longer than the primary symbol period, then the non-coherent achievable rate of primary decoding would approach that of the coherent case.
	The authors also considered the transmit precoder design for weighted total-rate maximization and transmit power minimization problems.
	\cite{Zhou2019a} explored how the number of transmit antennas, receive antennas, and symbol period ratio asymptotically influence the ergodic rate of primary and backscatter links.
	With multi-antenna at all ends, \cite{Wu2021a} optimized the transmit precoder to maximize the backscatter achievable rate under primary rate constraint.
	However, those paper only considered single tag scenario and the optimal tag multiple access scheme remains unknown.
	\cite{Xu2021a} proposed a \gls{noma}-based \gls{sr} and studied the receive combiner design when the receiver decodes in the order of equivalent channel strength.
	A \gls{tdma}-based \gls{sr} with energy harvesting constraints was also presented in \cite{Yang2021a}, and energy efficiency maximization was considered with respect to transmit power, reflection efficiency, and time allocation design.
	In \cite{Han2021}, random code-assisted backscatter multiple access was combined with \gls{sr}, and the authors evaluated the asymptotic \gls{sinr} performance using random matrix theory.

@@

	\emph{Third,} we characterize the achievable primary-(total-)backscatter rate region by iteratively optimizing the tag input distribution, the backscatter decision threshold, and the transmit precoder.
	For the input design, we propose a numerical method to evaluate the \gls{kkt} solutions by limits of sequences.
	For the threshold design, we derive the minimum number of decision thresholds to maximize the total backscatter rate, and obtain the optimal thresholds by \gls{dp} accelerated by \gls{smawk} algorithm.
	However, the optimal precoder design can be non-trivial and we may end up with a low-complexity suboptimal solution.

@@

\begin{section}{Backscatter Principles}
	\begin{figure}[!t]
		\centering
		\subfloat[Block Diagram]{
			\resizebox{0.8\columnwidth}{!}{
				\input{assets/block_diagram.tex}
			}
			\label{fi:block_diagram}
		}
		\\
		\subfloat[Equivalent Circuit]{
			\resizebox{0.95\columnwidth}{!}{
				\input{assets/equivalent_circuit.tex}
			}
			\label{fi:equivalent_circuit}
		}
		\\
		\subfloat[Scatter Model]{
			\resizebox{0.8\columnwidth}{!}{
				\input{assets/scatter_model.tex}
			}
			\label{fi:scatter_model}
		}
		\caption{Block diagram, equivalent circuit, and scatter model of a typical passive tag. The solid and dashed vectors represent signal and energy flows. The backscatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.}
	\end{figure}
	Passive backscatter devices (a.k.a., tags) harvest energy from and modulate information over surrounding \gls{rf} signal.
	As shown in Fig. \subref*{fi:block_diagram}, a typical passive tag consists of a scattering antenna, an energy harvester, an integrated receiver, a load-switching modulator, and on-chip components (e.g., micro-controller and sensors) \cite{Dobkin2012}. Its equivalent circuit is also given by Fig. \subref*{fi:equivalent_circuit}.
	When illuminated, the tag absorbs a portion of the impinging wave and scatters the rest back to the space.
	The absorbed signal can be used for source decoding and energy harvesting \cite{Kim2021a}, while the scattered signal can be decomposed into the \emph{structural} and \emph{antenna} mode components \cite{Hansen1989}.
	The structural mode scattering applies to general objects and is related to the antenna structure, shape and material, which contributes to environment multipath and can be covered by channel estimation \cite{Boyer2014}.
	On the other hand, the antenna mode scattering models the antenna radiation and depends on the antenna-load impedance mismatch, which can be used for backscatter modulation \cite{Boyer2012} or channel reconfiguration \cite{Wu2021b}.
	Fig. \subref*{fi:scatter_model} illustrates the scatter model.
	For a tag with $M$ candidate states, the reflection coefficient of state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is defined as
	\begin{footnote}
		It corresponds to a linear backscatter model where the reflection coefficient is irrelevant to incident electromagnetic field strength.
	\end{footnote}
	\begin{equation}
		\Gamma_m = \frac{Z_m - Z_{\mathrm{A}}^*}{Z_m + Z_{\mathrm{A}}},
		\label{eq:reflection_coefficient}
	\end{equation}
	where $Z_m$ is the load impedance at state $m$ and $Z_{\mathrm{A}}$ is the antenna input impedance.

@@

		Once the tag input combination is successfully decoded, the backscatter uncertainty can be eliminated and the equivalent channel for primary transmission can be updated by \eqref{eq:equivalent_channel}.
		Similar to above, the primary information function of input combination $x_{m_{\mathcal{K}}}$ is
		% TODO notation
		\begin{equation}
			I_{\mathrm{P}}(x_{m_{\mathcal{K}}};\boldsymbol{y}) \triangleq \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right),
			\label{eq:primary_information_function}
		\end{equation}
		the primary marginal information function associated with letter $x_{m_k}$ of tag $k$ is
		\begin{equation}
			I_{\mathrm{P},k}(x_{m_k};\boldsymbol{y}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I_{\mathrm{P}}(x_{m_{\mathcal{K}}};\boldsymbol{y}),
			\label{eq:primary_marginal_information_function}
		\end{equation}
		and the primary (ergodic) mutual information is
		\begin{equation}
			I_{\mathrm{P}}(x_{\mathcal{K}};\boldsymbol{y}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right).
			\label{eq:primary_mutual_information}
		\end{equation}

@@

\begin{section}{Input, Threshold, and Precoder Design}
	To characterize the achievable primary-(total-)backscatter rate region of Metascatter, we aim to maximize the weighted sum mutual information with respect to tag input probability distribution $\{\boldsymbol{p}_k\}$, decision threshold vector $\boldsymbol{t}$, and transmit precoder $\boldsymbol{w}$
	\begin{maxi!}
		{\scriptstyle{\{\boldsymbol{p}_k\},\boldsymbol{t},\boldsymbol{w}}}{I(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y})}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
		\addConstraint{\sum \nolimits_{m_k} P_k(x_{m_k})}{=1,}{\quad \forall k \in \mathcal{K}}{\label{co:sum_probability}}
		\addConstraint{P_k(x_{m_k})}{\ge 0,}{\quad \forall k \in \mathcal{K}, \ \forall m_k \in \mathcal{M}}{\label{co:nonnegative_probability}}
		\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P.}{\label{co:transmit_power}}
	\end{maxi!}
	Since problem \eqref{op:weighted_sum_rate} is not jointly convex, we propose a \gls{bcd} algorithm that iteratively updates $\{\boldsymbol{p}_k\}$, $\boldsymbol{t}$ and $\boldsymbol{w}$ until convergence.

	\begin{subsection}{Input Probability Distribution}
		For any fixed decision boundary $\boldsymbol{t}$ and transmit precoder $\boldsymbol{w}$, the equivalent \gls{dmtmac} can be formulated by \eqref{eq:dmtmac} and problem \eqref{op:weighted_sum_rate} boils down to
		\begin{maxi!}
			{\scriptstyle{\{\boldsymbol{p}_k\}}}{I(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y})}{\label{op:input_probability_distribution}}{}
			\addConstraint{\eqref{co:sum_probability},\eqref{co:nonnegative_probability},}
		\end{maxi!}
		which involves the product term $\prod_{k \in \mathcal{K}} P_k(x_{m_k})$ and is non-convex when $K > 1$.
		Interestingly, the total-rate optimal input design for general discrete memoryless \gls{mac} remains an open problem, and we instead propose a \gls{kkt} solution to problem \eqref{op:input_probability_distribution}.
		\begin{footnote}
			As pointed out in \cite{Buhler2011}, \gls{kkt} conditions are only necessary for total-rate optimality and these solutions may end up being saddle points.
		\end{footnote}
		\begin{proposition}
			The \gls{kkt} optimality conditions for problem \eqref{op:input_probability_distribution} are equivalent to, $\forall k \in \mathcal{K}$ and $\forall m_k \in \mathcal{M}$,
			\begin{subequations}
				\label{eq:input_kkt_condition}
				\begin{alignat}{2}
					I_k^\star(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) & = I^\star(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y}), \quad   &  & P_k^\star(x_{m_k}) > 0,\label{eq:probable_states} \\
					I_k^\star(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y}) & \le I^\star(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y}), \quad &  & P_k^\star(x_{m_k}) = 0.\label{eq:dropped_states}
				\end{alignat}
			\end{subequations}
			\label{pr:input_kkt_condition}
		\end{proposition}
